A Fredholm operator approach to the plate buckling problem

### 2018-08-21 doc/draft-01/08append.tex
Updating appendix

\begin{proof}
If $\bu = \nabla^{\perp} H_{0}(k r) = (\partial_{y} H_{0}(k r), 
-\partial_{x} H_{0}(k r))$, then
\begin{equation}
\nabla  p = (\Delta + k^2) \bu = (\Delta + k^2) \nabla^{\perp} 
H_{0} (k r) = 0 \, .
\end{equation}
Since $p\to 0$ as $r\to \infty$, we conclude that $p=0$.
\begin{align}
\ff_{1} &= 2\partial_{x} u_{1} \cos(\theta) + \left( \partial_{x} u_{2} + 
\partial_{y} u_{1} \right) \sin(\theta) \\
&= 2 \partial_{xy} H_{0}(k r) \cdot \frac{x}{r} +
\left[-\partial_{xx} H_{0}(k r) + \partial_{yy} H_{0}(k r) \right]
\cdot \frac{y}{r} \, .
\end{align}
Based on the mathematica script (radcond1.nb in our mathematica folder), we
get
\begin{equation}
\ff_{1} - i k u_{1} = \frac{ky}{r^2} \left( -kr \left(H_{0}(k r) + 
i H_{1}(k r)\right) +
2 H_{1}(k r)\right) \, .
\end{equation}
The result then follows from the asymptotic properties of Hankel functions since
\begin{equation}
H_{0}(z) = c \frac{e^{-iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \quad 
\text{and} \quad 
H_{1}(z) = i \cdot c \frac{e^{-iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \,,
\end{equation}
where $c$ is the same constant in both of these expansions.
\end{proof}

>>>>

\begin{proof}
If $\bu = \nabla^{\perp} H_{0}(k r) = (\partial_{y} H_{0}(k r), 
-\partial_{x} H_{0}(k r))$, then
\begin{equation}
\nabla  p = (\Delta + k^2) \bu = (\Delta + k^2) \nabla^{\perp} 
H_{0} (k r) = 0 \, .
\end{equation}
Since $p\to 0$ as $r\to \infty$, we conclude that $p=0$.
\begin{align}
\ff_{1} &= 2\partial_{x} u_{1} \cos(\theta) + \left( \partial_{x} u_{2} + 
\partial_{y} u_{1} \right) \sin(\theta) \\
&= 2 \partial_{xy} H_{0}(k r) \cdot \frac{x}{r} +
\left[-\partial_{xx} H_{0}(k r) + \partial_{yy} H_{0}(k r) \right]
\cdot \frac{y}{r} \, .
\end{align}
Based on the mathematica script (radcond1.nb in our mathematica folder), we
get
\begin{equation}
\ff_{1} - i k u_{1} = \frac{ky}{r^2} \left( -kr \left(H_{0}(k r) + 
i H_{1}(k r)\right) +
2 H_{1}(k r)\right) \, .
\end{equation}
The result then follows from the asymptotic properties of Hankel functions since
\begin{equation}
H_{0}(z) = c \frac{e^{iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \quad 
\text{and} \quad 
H_{1}(z) = -i \cdot c \frac{e^{iz}}{\sqrt{z}} + O(\frac{1}{z^{3/2}}) \,,
\end{equation}
where $c$ is the same constant in both of these expansions.
\end{proof}

The following lemma shows uniqueness for the impedance problem under
the assumption that $\bu$ is complex analytic.

\begin{lem}
Suppose that $\bu$ satisfies the radiation
condition~\cref{eq:radcond}. 
Suppose further that the stress tensor $\ff$ and $\bu$ satisfy
\begin{equation}
\ff + i k \bu = 0 \quad \xx \in \Gamma \, .
\end{equation}
Then $\bu \equiv 0$ for $\xx \in E$.
\end{lem}

\begin{proof}
Since $\bu$ satisfies the radiation condition at $\infty$ and $\ff = -ik u$
on $\Gamma$, it follows from~\cref{eq:repinfest} that
\begin{align}
&
\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) ds +
2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |e(\bu)|^2 \right)
dV +2 \text{Im} \left( k \int_{\Gamma} \bu \cdot \overline{\ff} ds  \right) \\
&= 
\int_{|\by|=r} \left( |\ff|^2 + |k|^2 |\bu|^2 \right) ds +
2 \text{Im}(k) \int_{E \cap B_{r}(0)} \left(|k|^2 |\bu|^2 + |e(\bu)|^2 \right)
dV +2 \left( |k|^{2} \int_{\Gamma} |\bu|^{2} \overline{\ff} ds  \right) = 0 
\, .
\end{align}
Since all the quantities are positive, this implies two things:
\begin{equation}
\int_{\Gamma} |\bu|^{2} = 0 \implies \bu = 0  \quad \xx \in \Gamma \, .
\end{equation}
along with the estimate
\begin{equation}
\lim_{r\to\infty} \int_{|\yy|=r} |\bu|^{2} ds \to 0 \, .
\end{equation}
The last equation implies the conditions for~\cref{lem:rellich}
are satisfied, from which we conclude that the components of $\bu$ 
are harmonic in $E$. 
Thus, the components of $\bu$ satisfy
\begin{equation}
\Delta u_{j}=  0 \quad \xx \in E \,, \quad \text{and} \quad
u_{j} = 0 \quad \xx \in \Gamma \, ,
\end{equation}
for $j=1,2$.
Then $\bu \equiv 0$ follows from the uniqueness of solutions to the 
Dirichlet problem for Laplace's equation.
\end{proof}
